Best Practices for Alchemical Free Energy Calculations: v\versionnumber

### 2020-01-21 paper/manuscript.tex
typos

    \caption{Alchemical intermediates are createtd by making the potential energy depend on a an additional variable $\lambda$ that interpolates between the chemical endpoints. In (\textbf{A}), at $\lambda=0$ the molecule is a fully interacting phenol and at $\lambda=1$,  a fully interacting benzene. (\textbf{B}) shows an illustration of the probability distribution of the potential energies as the switching function takes values of $\lambda=0$ to $\lambda=1$, intermediates are required for a sufficient overlap in potential energies to estimate a free energy difference between $\lambda=0$ and $\lambda=1$.

>>>>

    \caption{Alchemical intermediates are created by making the potential energy depend on a an additional variable $\lambda$ that interpolates between the chemical endpoints. In (\textbf{A}), at $\lambda=0$ the molecule is a fully interacting phenol and at $\lambda=1$,  a fully interacting benzene. (\textbf{B}) shows an illustration of the probability distribution of the potential energies as the switching function takes values of $\lambda=0$ to $\lambda=1$, intermediates are required for a sufficient overlap in potential energies to estimate a free energy difference between $\lambda=0$ and $\lambda=1$.
